Sample size

### 2021-04-16 scripts/r/sample-size/sample-size.Rmd
:recycle: - refactor sample size simulations

```{r functions}
simulate_data <- function(n, sd) {
  tibble(
    odds = rnorm(n, 1, sd),
    # no measurement error model for the simulation
    # es_se = rhcauchy(n, 0.15),
    team = letters[1:n]
  )
}

run_brm <- function(data) {
  priors <- c(
    prior(normal(0, 1), class = Intercept),
    prior(cauchy(0, 1), class = sd)
  )

  meta_bm <- brm(
    odds ~
      (1 | team),
    data = data,
    prior = priors,
    chain = 4,
    cores = 4,
    backend = "cmdstanr", threads = threading(4),
    control = list(adapt_delta = 0.9999, max_treedepth = 15),
  )

@@

run_simulations <- function(n, sd) {
  data <- simulate_data(n, sd)
  brm_model <- run_brm(data)
  return(brm_model)
}
```

@@

```{r team-sds, eval=FALSE, include=FALSE}
sds_20 <- map(
  sims_20$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()

sds_25 <- map(
  sims_25$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()

sds_30 <- map(
  sims_30$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()

sds_35 <- map(
  sims_35$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()

sds_40 <- map(
  sims_40$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()
```

>>>>

```{r functions}
simulate_data <- function(n, sd) {
  tibble::tibble(
    odds = rnorm(n, 1, sd),
    # no measurement error model for the simulation
    # es_se = rhcauchy(n, 0.15),
    team = letters[1:n]
  )
}

run_brm <- function(data) {
  priors <- c(
    brms::prior(normal(0, 1), class = Intercept),
    brms::prior(cauchy(0, 1), class = sd)
  )

  meta_bm <- brms::brm(
    odds ~
      (1 | team),
    data = data,
    prior = priors,
    chain = 4,
    cores = 4,
    backend = "cmdstanr", threads = brms::threading(4),
    control = list(adapt_delta = 0.9999, max_treedepth = 15),
  )

@@

run_simulations <- function(n, sd) {
  data <- simulate_data(n, sd)
  brm_model <- run_brm(data)

  sd_team <- purr::map(
    brm_model$model,
    ~tidybayes::spread_draws(.x, sd_team__Intercept) %>%
      dplyr::summarise(sd = sd(sd_team__Intercept)) %>%
      dplyr::pull()
  ) %>%
  unlist()

  return(sd_team)
}
```

@@
